---
title: "Chip-seq in Galaxy and R"
author: "Emily Chambers"
date: '`r format(Sys.time(), "Last modified: %d %b %Y")`'
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE)
```
# Hands-on chip-seq Analysis in Galaxy and R


# 1 Requirements
Install the package "ChIPpeakAnno" from Bioconductor:

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("ChIPpeakAnno")

```

# 2. Upload Data

Upload our MACS2 peak bed files that we downloaded from galaxy

```{r}
library(readr)
FOXA1_df <- read_tsv("data/FOXA1.bed", col_names = F)
FOXA1_df

ER_df <- read_tsv("data/ER.bed")
ER_df
```

# 3. Convert peaks into a GRanges object
A GRanges object form the GenomicRanges packages is a container for genomic locations and their associated annotations. We will use this data structure for the ChIP-seq peak coordinates.
```{r}
library(GenomicRanges) # load the GenomicRanges pakcage

FOXA1 <- GRanges(
  FOXA1_df$X1,
  IRanges(FOXA1_df$X2, FOXA1_df$X3),
  strand="*"
)

# we can add more data to each peak subsequently
names(FOXA1) <- paste("FOXA1_peak", 1:nrow(FOXA1_df), sep="_")
score(FOXA1) <- FOXA1_df$X8
  
# show the first and last lines of the GRanges object
FOXA1
```


